---
title: "First-Time Depositor (FTDs) Analysis"
author: "BI Team"
date: "2023-10-18"
output: 
  html_document:
    theme: default
    toc: true
    toc_float: true
    toc_depth: 3
    collapse: false
    smooth_scroll: false
---

<style type="text/css">

.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: Steelblue;
}
body{ 
      font-size: 13px;
      font-family::"Calibri (Body)";
      background-color:white;
  }
td {  
  font-size: 13px;
  font-family:"Calibri (Body)";
}
h1.title {
  font-size: 30px;
  font-family:"Calibri (Body)";
  color: Steelblue;
  font-weight: bold;
  text-align:center;
}

h4.author{ 
  font-size: 16px;
  color: black;
  font-family: "Calibri (Body)";
  font-style:italic;
  font-weight:normal;
} 
h4.date{ 
  font-size: 16px;
  font-family:"Calibri (Body)";
  color: black;
  font-style:italic;
  font-weight:normal;
} 
h1 {
  font-size: 27px;
  font-family:"Calibri (Body)";
  color:#30300A.;
  font-weight: bold;
}
h2 { 
   font-size: 25px;
   font-family:"Calibri (Body)";
   color:#30300A.;
   font-weight: bold;
}
h3{ 
  font-size: 21px;
  font-family:"Calibri (Body)";
  color:#30300A.;
  font-weight: bold;
}
h4{ 
  font-size: 19px;
  font-family:"Calibri (Body)";
  color:#30300A.;
  font-weight: bold;
}
h5{ 
  font-size: 17px;
  font-family:"Calibri (Body)";
  color:#30300A.;
  font-weight: bold;
}
code.r{ 
    font-size: 11px;
}
pre { 
    font-size: 11px;
    width: 600px;
    border:0;
    text-align:top;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r,include=FALSE}
if(!require(odbc)) install.packages("odbc")
if(!require(DBI)) install.packages("DBI")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(dplyr)) install.packages("dplyr")
if(!require(keyring)) install.packages("keyring")
if(!require(duckdb)) install.packages("duckdb")
if(!require(arrow)) install.packages("arrow")
if(!require(dbplyr)) install.packages("dbplyr")
if(!require(tidyr)) install.packages("tidyr")
if(!require(DescTools)) install.packages("DescTools")
if(!require(scales)) install.packages("scales")
if(!require(rstatix)) install.packages("rstatix")

## duckdb
# Define the database name
db_name <- "your_database_name"

# Define the directory where you want to store the database
db_directory <- "C:/Users/raymart.biasbas/Documents/Proyekto/First Deposit vs Second Deposit"

# Create the full database path
db_path <- file.path(db_directory, paste0(db_name, ".db"))

duckdb_conn <- dbConnect(duckdb(), dbname = db_path)


#Connect to DWH
# dwh_conn <- dbConnect(odbc(), "DWH", uid = key_get("db_user"),
#     pwd = key_get("db_pass"), encoding = "UTF-8")
```

```{r, include=FALSE}
# df <- dbGetQuery(dwh_conn,"
#                  			SELECT
#               				dp.Id
#               				,dc.Code Currency
#                               ,dateadd(hour,8,FirstDepositDate) FTD_Date
#                               ,dp.FirstDepositAmount/FirstDepositExchRate FTD_Amount_USD
#                               ,dpl.Viplevel
#                               ,sec_dep.STD_Date
#                               ,isnull(sec_dep.STD_Amount_USD,0) STD_Amount_USD
#                               FROM DWH.WH.DimPlayer dp with (nolock)
#                               INNER JOIN DWH.WH.DimCurrency dc with (nolock) on dp.CurrencyID = dc.Id
#                               INNER JOIN DWH.WH.DimLoyaltyProgramLevel dpl with  (nolock) on dp.VIPLevelId = dpl.Id
#                               LEFT JOIN (
#                               	SELECT
#                               	pt.PlayerId
#                               	,dateadd(hour,8,pt.StartTime) STD_Date
#                               	,pt.Amount/isnull(fx.rate,1) STD_Amount_USD
#                               	,row_number() over (partition by pt.playerid order by pt.StartTime) rankie
#                               	FROM DWH.Payment.PaymentTransaction pt with (nolock)
#                                   INNER JOIN DWH.WH.DimTime dt with (nolock) on pt.TimeId = dt.Id
#                                   INNER JOIN DWH.WH.FactExchangeRates fx with (nolock) on dt.TimeId12MNUTC0 = fx.TimeId
#                                   and pt.CurrencyId = fx.CurrencyId
#                                   WHERE 1=1
#                                   AND pt.StartTime >= dateadd(hour,-8,'2023-01-01')
#                               AND pt.StartTime < dateadd(hour,-8,'2023-10-01')
#                               AND pt.TransactionTypeId in (1,27)
#                           	  AND pt.StatusId = 3
#                           ) sec_dep on dp.Id = sec_dep.PlayerId and rankie = 2
#                           WHERE 1=1
#                           AND dp.BrandId = 2
#                           AND dp.IsInternalAccount = 0
#                           AND dp.City != 'm_test_only'
#                           AND NOT dp.RisklevelName in ('Affiliate','Test')
#                           AND dc.Code in ('VND','CNY','THB','IDR')
#                           AND dp.FirstDepositDate >= dateadd(hour,-8,'2023-01-01')
#                           AND dp.FirstDepositDate < dateadd(hour,-8,'2023-10-01')
# ")
# 
# total_dep <- dbGetQuery(dwh_conn,"
#                         SELECT
#                         pt.PlayerId
#                         ,sum(pt.Amount/isnull(fx.rate,1)) Deposit_Amount_USD
#                         FROM DWH.Payment.PaymentTransaction pt with (nolock)
#                         INNER JOIN DWH.WH.DimPlayer dp with (nolock) on pt.PlayerID = dp.Id
#                         INNER JOIN DWH.WH.DimCurrency dc with (nolock) on dp.CurrencyID = dc.Id
#                         INNER JOIN DWH.WH.DimTime dt with (nolock) on pt.TimeId = dt.Id
#                         INNER JOIN DWH.WH.FactExchangeRates fx with (nolock) on dt.TimeId12MNUTC0 = fx.TimeId
#                         and pt.CurrencyId = fx.CurrencyId
#                         WHERE 1=1
#                         AND pt.StartTime >= dateadd(hour,-8,'2023-01-01')
#                         AND pt.StartTime < dateadd(hour,-8,'2023-10-01')
#                         AND pt.TransactionTypeId in (1,27)
#                         AND pt.StatusId = 3
#                         AND dp.BrandId = 2
#                         AND dp.IsInternalAccount = 0
#                         AND dp.City != 'm_test_only'
#                         AND NOT dp.RisklevelName in ('Affiliate','Test')
#                         AND dc.Code in ('VND','CNY','THB','IDR')
#                         AND dp.FirstDepositDate >= dateadd(hour,-8,'2023-01-01')
#                         AND dp.FirstDepositDate < dateadd(hour,-8,'2023-10-01')
#                         GROUP BY
#                         pt.PlayerId"
# )
# 
# 
# dbDisconnect(dwh_conn)
# 
# saveRDS(df,file = "FTD_Data.RDS")
# saveRDS(total_dep,file = "Total_Deposit.RDS")

df <- readRDS("FTD_Data.RDS")
total_dep <-readRDS("Total_Deposit.RDS") 

dbWriteTable(duckdb_conn,"FTD_data",df,overwrite = TRUE)
dbWriteTable(duckdb_conn,"Total_Dep_data",total_dep,overwrite = TRUE)


rm(df)
rm(total_dep)



df_pivoted <- tbl(duckdb_conn,"FTD_data")  |>
  pivot_longer(cols = c('FTD_Amount_USD','STD_Amount_USD')
               ,names_to = "DepositType"
               ,values_to = "Deposit_USD"
               ) |>
  mutate(has_STD = ifelse(is.na(STD_Date),0,1)) |>
  collect()


dbWriteTable(duckdb_conn,"FTD_data_pivoted",df_pivoted,overwrite = TRUE)

rm(df_pivoted)

df_pivoted <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(Deposit_USD > 0) |>
  collect()

df_summary <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(Deposit_USD > 0) |>
  group_by(DepositType) |>
  summarize(UAP = n_distinct(if_else(Deposit_USD > 0, Id, NULL))
            ,mean = mean(Deposit_USD)
            ,min = min(Deposit_USD)
            ,Q1 = quantile(Deposit_USD,0.25)
            ,median = median(Deposit_USD)
            ,Q3 = quantile(Deposit_USD,0.75)
            ,max = max(Deposit_USD)
            ,total = sum(Deposit_USD)) |>
  collect()

df_pivoted1 <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(has_STD == 1) |>
  collect()

df_summary1 <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(has_STD == 1) |>
  group_by(DepositType) |>
  summarize(UAP = n_distinct(if_else(Deposit_USD > 0, Id, NULL))
            ,mean = mean(Deposit_USD)
            ,min = min(Deposit_USD)
            ,Q1 = quantile(Deposit_USD,0.25)
            ,median = median(Deposit_USD)
            ,Q3 = quantile(Deposit_USD,0.75)
            ,max = max(Deposit_USD)
            ,total = sum(Deposit_USD)) |>
  collect()



df_curr_summary <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(Deposit_USD > 0) |>
  group_by(DepositType,Currency) |>
  summarize(UAP = n_distinct(Id)
            ,mean = mean(Deposit_USD)
            ,min = min(Deposit_USD)
            ,Q1 = quantile(Deposit_USD,0.25)
            ,median = median(Deposit_USD)
            ,Q3 = quantile(Deposit_USD,0.75)
            ,max = max(Deposit_USD)
            ,total = sum(Deposit_USD)) |>
  ungroup() |>
  pivot_wider(names_from = DepositType
              ,values_from = c(mean,min,Q1,median,Q3,max,total)
              ,names_sep = " "
              ,values_fill = 0) |>
  group_by(Currency) |>
  summarise_all(sum) |>
  collect()

df_curr_summary1 <- tbl(duckdb_conn,"FTD_data_pivoted") |>
  filter(has_STD == 1) |>
  group_by(DepositType,Currency) |>
  summarize(UAP = n_distinct(Id)
            ,mean = mean(Deposit_USD)
            ,min = min(Deposit_USD)
            ,Q1 = quantile(Deposit_USD,0.25)
            ,median = median(Deposit_USD)
            ,Q3 = quantile(Deposit_USD,0.75)
            ,max = max(Deposit_USD)
            ,total = sum(Deposit_USD)) |>
  ungroup() |>
  pivot_wider(names_from = DepositType
              ,values_from = c(mean,min,Q1,median,Q3,max,total)
              ,names_sep = " "
              ,values_fill = 0) |>
  group_by(Currency) |>
  summarise_all(sum) |>
  collect()

total_dep <- tbl(duckdb_conn,"Total_Dep_data") |>
  collect()


transposed <- as.data.frame(t(df_summary))

colnames(transposed) <- transposed[1,]

transposed <- transposed[-1,] 

diff <- transposed|>
  mutate(diff = as.numeric(as.numeric(FTD_Amount_USD)-as.numeric(STD_Amount_USD)))


overall_test <- t.test(Deposit_USD~DepositType, data = df_pivoted, alternative = 'two.sided')

overall_test1 <- t.test(Deposit_USD~DepositType, data = df_pivoted1,paired =TRUE ,alternative = 'two.sided')

currency_test <- df_pivoted |>
  filter(Deposit_USD > 0) |>
  group_by(Currency) |>
  rstatix::t_test(Deposit_USD~DepositType, alternative  = 'two.sided',paired = FALSE)

currency_test1 <- df_pivoted |>
  filter(!is.na(Deposit_USD)) |>
  group_by(Currency) |>
  rstatix::t_test(Deposit_USD~DepositType, alternative  = 'two.sided',paired = FALSE)



z.score <- function(x) coalesce((x-mean(x,na.rm=T))/sd(x,na.rm = T),0)
upper <- function(x) quantile(x,0.75) + (1.5*IQR(x))

df <- tbl(duckdb_conn,"FTD_data") |>
  collect() |>
  mutate(has_STD =  ifelse(!is.na(STD_Date),1,0)
         ,FTDq3 = quantile(FTD_Amount_USD,0.75)
         ,STDq3 = quantile(STD_Amount_USD,0.75)
         ,FTDz = z.score(FTD_Amount_USD)
         ,STDz = z.score(STD_Amount_USD)
         ,FTDu = upper(FTD_Amount_USD)
         ,STDu = upper(STD_Amount_USD)
         ,FTDoz = ifelse(abs(FTDz) <= 3.5,0,1)
         ,FTDou = ifelse(FTD_Amount_USD <=FTDu,0,1)
         ,STDoz = ifelse(abs(STDz) <= 3.5,0,1)
         ,STDou = ifelse(STD_Amount_USD <=STDu,0,1)
) 

df_25pct <- df |>
  filter(FTD_Amount_USD >=FTDq3)

df_25pct_summary <- df_25pct |> 
  group_by(Viplevel) |>
  summarise(UAP = n_distinct(Id))

```


# Set Up
This analysis aims to determine whether the difference in the first deposit amount is significantly higher compared to the second deposit. Additionally, will identify which FTD's are more likely to make second deposit. Furthermore, it will investigate whether currency and VIP Level has a significant effect on FTDs' making their second deposit.

The data used includes all First-Time Depositors (FTDs) from January 1, 2023, to September 30, 2023. The metrics that will be used are the FTD amount and the STD amount for the period from January 1, 2023, to September 30, 2023. Moreover, first deposit amount and second deposit amount are in USD.

# Overview

This analysis investigates the deposit behavior of First-Time Depositors (FTDs) during the period from January 1, 2023, to September 30, 2023. It examines several critical aspects to gain insights into what drives FTDs' decisions regarding making a second deposit.

Firstly, a noteworthy difference was observed between the amounts of the first and second deposits made by FTDs. On average, FTDs tend to increase their deposit amounts over time, signifying a pattern of growing financial engagement.

Another key factor examined was the influence of VIP levels on FTDs' likelihood of making a second deposit. This analysis unveiled a strong correlation between VIP tiers and second deposit behavior. Specifically, Diamond-tier FTDs exhibited a 100% likelihood of making a second deposit, while other VIP tiers also displayed significant probabilities.

The currency emerged as another influential factor. Different currencies significantly affect FTDs' propensity to make a second deposit. VND and IDR FTDs, in particular, demonstrated high probabilities of making a second deposit, underlining the substantial role of currency preferences in shaping user behavior.

In summary, this analysis provides valuable insights: FTDs tend to increase their deposit amounts over time, VIP levels strongly impact second deposit behavior, and the currency plays a crucial role in shaping deposit patterns. These findings shed light on the factors that drive FTDs' financial engagement and contribute to their loyalty.

# Analysis of First-Time Depositors (FTDs)
## Overall

```{r, include=FALSE}
intro <- paste0("In this section, will analyze whether there is a statistically significant difference between the first deposit and second deposit amounts of First-Time Depositors (FTDs). Additionally, will specifically examine the subset of FTDs who have made a second deposit and determine if there is a significant difference between their first deposit amount and second deposit amount. Furthermore, will assess whether the VIP level of the FTDs has a significant effect on their likelihood of making a second deposit. This analysis aims to provide insights into the factors that influence FTDs' second deposit behavior. The data used in this analysis spans from January 1, 2023, to September 30, 2023.")
```

`r intro`

```{r,include=FALSE}
total_diff_overall <- (df_summary$total[tolower(df_summary$DepositType) %like% 'ftd%'] - df_summary$total[tolower(df_summary$DepositType) %like% 'std%'])


mean_diff_overall <- (df_summary$mean[tolower(df_summary$DepositType) %like% 'ftd%'] - df_summary$mean[tolower(df_summary$DepositType) %like% 'std%'])

high_low <- ifelse(mean_diff_overall > 0,'higher','lower')

mean_diff_overall <- mean_diff_overall |> scales::dollar()

median_diff_overall <- (df_summary$median[tolower(df_summary$DepositType) %like% 'ftd%'] - df_summary$median[tolower(df_summary$DepositType) %like% 'std%'])

median_diff_overall <- median_diff_overall |> scales::dollar()

cond_overall <- ifelse(overall_test$p.value <= 0.05
                       , paste0("Notably, The FTDs first deposit is significantly ", high_low," compared to second deposit with a mean difference of<b> ",mean_diff_overall," </b> and a median difference of<b> ",median_diff_overall,"</b>.")
                       ,paste0("Notably, The FTDs first deposit is ", high_low," compared to second deposit with a mean difference of<b> ",mean_diff_overall," </b> and a median difference of<b> ",median_diff_overall," </b>. However the difference is not statistically significant."))


p1 <- paste0("There is a total of <b>", df_summary$UAP[tolower(df_summary$DepositType) %like% "ftd%"] |> scales::comma()," </b>First-Time Depositors (FTDs). The FTDs collectively accumulated a total deposit amount of <b>",sum(total_dep$Deposit_Amount_USD) |> scales::dollar(),"</b>, with <b>",paste0((sum(df_summary$total[tolower(df_summary$DepositType) %like% 'ftd%'])/sum(total_dep$Deposit_Amount_USD)) |> scales::percent(accuracy = 0.01)," (",sum(df_summary$total[tolower(df_summary$DepositType) %like% 'ftd%']) |> scales::dollar(),")"),"</b> of this amount came from their first deposit, and <b>",paste0((sum(df_summary$total[tolower(df_summary$DepositType) %like% 'std%'])/sum(total_dep$Deposit_Amount_USD)) |> scales::percent(accuracy = 0.01)," (",sum(df_summary$total[tolower(df_summary$DepositType) %like% 'std%']) |> scales::dollar(),")"),"</b>  originated from their second deposit."
             ,"The mean first deposit amount for FTDs is <b>",df_summary$mean[tolower(df_summary$DepositType) %like% 'ftd%'] |> scales::dollar(),"</b> with a median of <b>",df_summary$median[tolower(df_summary$DepositType) %like% 'ftd%'] |> scales::dollar(), "</b>. In contrast, the mean second deposit amount is <b>",df_summary$mean[tolower(df_summary$DepositType) %like% 'std%'] |> scales::dollar(),"</b> and a median of <b>",df_summary$median[tolower(df_summary$DepositType) %like% 'std%'] |> scales::dollar(),"</b>."
             ,cond_overall)

```

`r p1`

```{r,include=FALSE}
#######
total_diff_overall1 <- (df_summary1$total[tolower(df_summary1$DepositType) %like% 'ftd%'] - df_summary1$total[tolower(df_summary1$DepositType) %like% 'std%'])

######


mean_diff_overall1 <- (df_summary1$mean[tolower(df_summary1$DepositType) %like% 'ftd%'] - df_summary1$mean[tolower(df_summary1$DepositType) %like% 'std%'])

high_low1 <- ifelse(mean_diff_overall1 > 0,'higher','lower')

mean_diff_overall1 <- mean_diff_overall1 |> scales::dollar()

median_diff_overall1 <- (df_summary1$median[tolower(df_summary1$DepositType) %like% 'ftd%'] - df_summary1$median[tolower(df_summary1$DepositType) %like% 'std%'])

median_diff_overall1 <- median_diff_overall1 |> scales::dollar()

cond_overall1 <- ifelse(overall_test1$p.value <= 0.05
                       , paste0(" the FTDs first deposit is significantly ", high_low1," compared to second deposit with a mean difference of<b> ",mean_diff_overall1," </b> and a median difference of<b> ",median_diff_overall1,"</b>.")
                       ,paste0(" the FTDs first deposit is ", high_low," compared to second deposit with a mean difference of<b> ",mean_diff_overall1," </b> and a median difference of<b> ",median_diff_overall1," </b>. However the difference is not statistically significant."))


std_uap1 <- df_summary$UAP[tolower(df_summary$DepositType) %like% 'std%'] |> scales::comma()

std_pct1 <- (df_summary$UAP[tolower(df_summary$DepositType) %like% 'std%']/df_summary$UAP[tolower(df_summary$DepositType) %like% 'ftd%']) |> scales::percent()

ftd_mean1 <- df_summary1$mean[tolower(df_summary1$DepositType) %like% 'ftd%'] |> scales::dollar()
std_mean1 <- df_summary1$mean[tolower(df_summary1$DepositType) %like% 'std%'] |> scales::dollar()
ftd_median1 <- df_summary1$median[tolower(df_summary1$DepositType) %like% 'ftd%'] |> scales::dollar()
std_median1 <- df_summary1$median[tolower(df_summary1$DepositType) %like% 'std%'] |> scales::dollar()
ftd_tot1 <- df_summary1$total[tolower(df_summary1$DepositType) %like% 'ftd%'] |> scales::dollar()
std_tot1 <- df_summary1$total[tolower(df_summary1$DepositType) %like% 'std%'] |> scales::dollar()


p2 <- paste0("When looking at FTDs with second deposits, only <b>" ,paste0(std_pct1," (",std_uap1,")"), "</b> of the FTDs has made second deposits."
," These FTDs generated a total of <b>",ftd_tot1, "</b> first deposit amount with mean at <b>",ftd_mean1,"</b> and median at <b>",ftd_median1,"</b>."
," Moreover,",cond_overall1)
```
`r p2`


```{r,include=FALSE}
model <- lm(STD_Amount_USD~Viplevel, data = df)

anova <- anova(model)

anova_pval <- anova$`Pr(>F)`[1]

cont_tbl <- table(df$Viplevel,df$has_STD)

prop <- prop.table(cont_tbl,margin = 1) |> as.data.frame()

prop$Freq[prop$Var1 == 'Diamond' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01)

chsq <- chisq.test(cont_tbl)


p3 <- if(anova_pval <= 0.05) {
  paste0("Based on ANOVA analysis, there is a strong evidence that VIP level significantly affects the likelihood of FTDs making a second deposit. This implies that the FTDs' VIP level plays a notable role in determining whether FTDs' will make a second deposit.")
} else {
    paste0("Based on ANOVA analysis, there is a strong evidence that VIP level does not affect the likelihood of FTDs making a second deposit. This implies that the FTDs' VIP level does not play a notable role in determining whether FTDs' will make a second deposit.")
}
p3.1 <- paste0("Diamond-tier FTDs have a <b>", prop$Freq[prop$Var1 == 'Diamond' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b> likelihood of making a second deposit, Platinum-tier FTDs exhibit a high likelihood at <b>",prop$Freq[prop$Var1 == 'Platinum' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b>, Gold-tier FTDs follow closely at <b>",prop$Freq[prop$Var1 == 'Gold' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b>, Silver-tier FTDs also show a significant likelihood at <b>",prop$Freq[prop$Var1 == 'Silver' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b> for making second deposits, and Bronze-tier FTDs has <b>",prop$Freq[prop$Var1 == 'Bronze' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b> likelihood of making second deposit. Importantly, these likelihoods are statistically significant, highlighting the considerable impact of VIP levels on FTDs' second deposit behavior.")
```
`r paste(p3,p3.1)`

```{r, include = FALSE}
p4 <- paste0("It is important to note that, despite the fact that 75 percent of the FTDs' first deposit are below <b>",df_summary$Q3[tolower(df_summary$DepositType) %like% 'ftd%'] |> scales::dollar(accuracy = 0.01),"</b> and second deposit below <b>",df_summary$Q3[tolower(df_summary$DepositType) %like% 'std%']|> scales::dollar(accuracy = 0.01),"</b>, no outliers are observed in the data. The skewed distribution is indicative of the majority of values clustering towards the lower end, which contributes to the skewness, rather than the existence of extreme or outlier values.")
```
`r p4`

## Currency

```{r,include=FALSE}

intro <- paste0("In this section, will conduct an analysis to determine whether there is a statistically significant difference between the First-Time Depositors' (FTDs) first deposit amounts and second deposit amounts within each of the different currencies. Additionally, will specifically focus on the subset of FTDs who have made a second deposit and assess if there is a significant difference between their first and second deposit amounts in each of the currencies. This analysis aims to understand if the currency has a significant effect on FTDs making a second deposit. The data used in this analysis spans from January 1, 2023, to September 30, 2023.")
```
`r intro`

```{r, include=FALSE}
total_diff_currency <- (df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "VND"]- df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "VND"])


mean_diff_currency <- (df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "VND"]- df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "VND"])

mean_diff_currency <- mean_diff_currency |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency < 0,'increase','decrease')

median_diff_currency <- (df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "VND"]- df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "VND"])

median_diff_currency <- median_diff_currency |> scales::dollar()

cond_currency <- ifelse(currency_test$p[currency_test$Currency == 'VND'] <= 0.05
                       , paste0("  the first deposit for these FTDs is significantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>.",
                                "This data suggests a substantial ",inc_dec," in deposit amounts between the first and second deposits for FTDs in VND, highlighting distinct deposit behavior in this currency.")
                       , paste0("  the first deposit for these FTDs is insignificantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>."))

p1 <- paste0('In VND, a total of <b>',df_curr_summary$UAP[df_curr_summary$Currency == "VND"] |> scales::comma(),"</b> First-Time Depositors (FTDs)"
             ," collectively generated a total first deposit amount of <b>",df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(), "</b> and a median of <b>",df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(),"</b>."
             ," Additionally, they accumulated a total second deposit amount of <b>",df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "VND"] |> scales::dollar(),"</b>."
             ," Notably,",cond_currency)
```
`r p1`

```{r, include=FALSE}

total_diff_currency1 <- (df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "VND"]- df_curr_summary1$`total STD_Amount_USD`[df_curr_summary1$Currency == "VND"])


mean_diff_currency1 <- (df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "VND"]- df_curr_summary1$`mean STD_Amount_USD`[df_curr_summary1$Currency == "VND"])

mean_diff_currency1 <- mean_diff_currency1 |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency1 > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency1 > 0,'increase','decrease')

median_diff_currency1 <- (df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "VND"]- df_curr_summary1$`median STD_Amount_USD`[df_curr_summary1$Currency == "VND"])

median_diff_currency1 <- median_diff_currency1 |> scales::dollar()

cond_currency1 <- if(currency_test1$p[currency_test1$Currency == 'VND'] <= 0.05) {
  paste(" Moreover, the FTDs' first deposit amount is significantly ",high_low_curr," compared to the second deposit amount.")
} else {
  paste(" Moreover, the FTDs' first deposit amount is insignificantly ",high_low_curr," compared to the second deposit amount.")
}
  
p2 <- paste0("Specifically, among those who made second deposits in VND, a total of <b>",df_curr_summary1$UAP[df_curr_summary1$Currency == "VND"] |> scales::comma(),"</b> FTDs generated a cumulative first deposit amount of <b>",df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "VND"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "VND"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "VND"] |> scales::dollar(),"</b>."
             ,cond_currency1)

```
`r p2`

```{r, include=FALSE}
total_diff_currency <- (df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "IDR"]- df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "IDR"])


mean_diff_currency <- (df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "IDR"]- df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "IDR"])

mean_diff_currency <- mean_diff_currency |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency < 0,'increase','decrease')

median_diff_currency <- (df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "IDR"]- df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "IDR"])

median_diff_currency <- median_diff_currency |> scales::dollar()

cond_currency <- ifelse(currency_test$p[currency_test$Currency == 'IDR'] <= 0.05
                       , paste0("  the first deposit for these FTDs is significantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>.",
                                "This data suggests a substantial ",inc_dec," in deposit amounts between the first and second deposits for FTDs in IDR, highlighting distinct deposit behavior in this currency.")
                       , paste0("  the first deposit for these FTDs is insignificantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>."))

p3 <- paste0('In IDR, a total of <b>',df_curr_summary$UAP[df_curr_summary$Currency == "IDR"] |> scales::comma(),"</b> First-Time Depositors (FTDs)"
             ," collectively generated a total first deposit amount of <b>",df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(), "</b> and a median of <b>",df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(),"</b>."
             ," Additionally, they accumulated a total second deposit amount of <b>",df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "IDR"] |> scales::dollar(),"</b>."
             ," Notably,",cond_currency)
```
`r p3`

```{r, include=FALSE}

total_diff_currency1 <- (df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"]- df_curr_summary1$`total STD_Amount_USD`[df_curr_summary1$Currency == "IDR"])


mean_diff_currency1 <- (df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"]- df_curr_summary1$`mean STD_Amount_USD`[df_curr_summary1$Currency == "IDR"])

mean_diff_currency1 <- mean_diff_currency1 |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency1 > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency1 > 0,'increase','decrease')

median_diff_currency1 <- (df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"]- df_curr_summary1$`median STD_Amount_USD`[df_curr_summary1$Currency == "IDR"])

median_diff_currency1 <- median_diff_currency1 |> scales::dollar()

cond_currency1 <- if(currency_test1$p[currency_test1$Currency == 'IDR'] <= 0.05) {
  paste(" Moreover, the FTDs' first deposit amount is significantly ",high_low_curr," compared to the second deposit amount.")
} else {
  paste(" Moreover, the FTDs' first deposit amount is insignificantly ",high_low_curr," compared to the second deposit amount.")
}
  
p4 <- paste0("Specifically, among those who made second deposits in IDR, a total of <b>",df_curr_summary1$UAP[df_curr_summary1$Currency == "IDR"] |> scales::comma(),"</b> FTDs generated a cumulative first deposit amount of <b>",df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "IDR"] |> scales::dollar(),"</b>."
             ,cond_currency1)

```
`r p4`


```{r, include=FALSE}
total_diff_currency <- (df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "CNY"]- df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "CNY"])


mean_diff_currency <- (df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "CNY"]- df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "CNY"])

mean_diff_currency <- mean_diff_currency |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency < 0,'increase','decrease')

median_diff_currency <- (df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "CNY"]- df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "CNY"])

median_diff_currency <- median_diff_currency |> scales::dollar()

cond_currency <- ifelse(currency_test$p[currency_test$Currency == 'CNY'] <= 0.05
                       , paste0("  the first deposit for these FTDs is significantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>.",
                                "This data suggests a substantial ",inc_dec," in deposit amounts between the first and second deposits for FTDs in CNY, highlighting distinct deposit behavior in this currency.")
                       , paste0("  the first deposit for these FTDs is insignificantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>."))

p5 <- paste0('In CNY, a total of <b>',df_curr_summary$UAP[df_curr_summary$Currency == "CNY"] |> scales::comma(),"</b> First-Time Depositors (FTDs)"
             ," collectively generated a total first deposit amount of <b>",df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(), "</b> and a median of <b>",df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(),"</b>."
             ," Additionally, they accumulated a total second deposit amount of <b>",df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "CNY"] |> scales::dollar(),"</b>."
             ," Notably,",cond_currency)
```
`r p5`

```{r, include=FALSE}

total_diff_currency1 <- (df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"]- df_curr_summary1$`total STD_Amount_USD`[df_curr_summary1$Currency == "CNY"])


mean_diff_currency1 <- (df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"]- df_curr_summary1$`mean STD_Amount_USD`[df_curr_summary1$Currency == "CNY"])

mean_diff_currency1 <- mean_diff_currency1 |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency1 > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency1 > 0,'increase','decrease')

median_diff_currency1 <- (df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"]- df_curr_summary1$`median STD_Amount_USD`[df_curr_summary1$Currency == "CNY"])

median_diff_currency1 <- median_diff_currency1 |> scales::dollar()

cond_currency1 <- if(currency_test1$p[currency_test1$Currency == 'CNY'] <= 0.05) {
  paste(" Moreover, the FTDs' first deposit amount is significantly ",high_low_curr," compared to the second deposit amount.")
} else {
  paste(" Moreover, the FTDs' first deposit amount is insignificantly ",high_low_curr," compared to the second deposit amount.")
}
  
p6 <- paste0("Specifically, among those who made second deposits in CNY, a total of <b>",df_curr_summary1$UAP[df_curr_summary1$Currency == "CNY"] |> scales::comma(),"</b> FTDs generated a cumulative first deposit amount of <b>",df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "CNY"] |> scales::dollar(),"</b>."
             ,cond_currency1)

```
`r p6`


```{r, include=FALSE}
total_diff_currency <- (df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "THB"]- df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "THB"])


mean_diff_currency <- (df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "THB"]- df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "THB"])

mean_diff_currency <- mean_diff_currency |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency < 0,'increase','decrease')

median_diff_currency <- (df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "THB"]- df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "THB"])

median_diff_currency <- median_diff_currency |> scales::dollar()

cond_currency <- ifelse(currency_test$p[currency_test$Currency == 'THB'] <= 0.05
                       , paste0("  the first deposit for these FTDs is significantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>.",
                                "This data suggests a substantial ",inc_dec," in deposit amounts between the first and second deposits for FTDs in THB, highlighting distinct deposit behavior in this currency.")
                       , paste0("  the first deposit for these FTDs is insignificantly ", high_low1,"  compared to the second deposit, with a mean difference of <b> ",mean_diff_currency," </b> and a median difference of <b> ",median_diff_currency,"</b>."))

p7 <- paste0('In THB, a total of <b>',df_curr_summary$UAP[df_curr_summary$Currency == "THB"] |> scales::comma(),"</b> First-Time Depositors (FTDs)"
             ," collectively generated a total first deposit amount of <b>",df_curr_summary$`total FTD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean FTD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(), "</b> and a median of <b>",df_curr_summary$`median FTD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(),"</b>."
             ," Additionally, they accumulated a total second deposit amount of <b>",df_curr_summary$`total STD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary$`mean STD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary$`median STD_Amount_USD`[df_curr_summary$Currency == "THB"] |> scales::dollar(),"</b>."
             ," Notably,",cond_currency)
```
`r p7`

```{r, include=FALSE}

total_diff_currency1 <- (df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "THB"]- df_curr_summary1$`total STD_Amount_USD`[df_curr_summary1$Currency == "THB"])


mean_diff_currency1 <- (df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "THB"]- df_curr_summary1$`mean STD_Amount_USD`[df_curr_summary1$Currency == "THB"])

mean_diff_currency1 <- mean_diff_currency1 |> scales::dollar()

high_low_curr <- ifelse(mean_diff_currency1 > 0,'higher','lower')
inc_dec <-ifelse(mean_diff_currency1 > 0,'increase','decrease')

median_diff_currency1 <- (df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "THB"]- df_curr_summary1$`median STD_Amount_USD`[df_curr_summary1$Currency == "THB"])

median_diff_currency1 <- median_diff_currency1 |> scales::dollar()

cond_currency1 <- if(currency_test1$p[currency_test1$Currency == 'THB'] <= 0.05) {
  paste(" Moreover, the FTDs' first deposit amount is significantly ",high_low_curr," compared to the second deposit amount.")
} else {
  paste(" Moreover, the FTDs' first deposit amount is insignificantly ",high_low_curr," compared to the second deposit amount.")
}
  
p8 <- paste0("Specifically, among those who made second deposits in THB, a total of <b>",df_curr_summary1$UAP[df_curr_summary1$Currency == "THB"] |> scales::comma(),"</b> FTDs generated a cumulative first deposit amount of <b>",df_curr_summary1$`total FTD_Amount_USD`[df_curr_summary1$Currency == "THB"] |> scales::dollar(),"</b>, with a mean of <b>",df_curr_summary1$`mean FTD_Amount_USD`[df_curr_summary1$Currency == "THB"] |> scales::dollar(),"</b> and a median of <b>",df_curr_summary1$`median FTD_Amount_USD`[df_curr_summary1$Currency == "THB"] |> scales::dollar(),"</b>."
             ,cond_currency1)

```
`r p8`

```{r,include=FALSE}
model <- lm(STD_Amount_USD~Currency, data = df)

anova <- anova(model)

anova_pval <- anova$`Pr(>F)`[1]

cont_tbl <- table(df$Currency,df$has_STD)

prop <- prop.table(cont_tbl,margin = 1) |> as.data.frame()

prop$Freq[prop$Var1 == 'Diamond' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01)

chsq <- chisq.test(cont_tbl)


p9 <- if(anova_pval <= 0.05) {
  paste0("Based on ANOVA analysis, there is a strong evidence that currency significantly affects the likelihood of FTDs making a second deposit. This implies that the FTDs' currency plays a notable role in determining whether FTDs' will make a second deposit.")
} else {
    paste0("Based on ANOVA analysis, there is a strong evidence that currency does not affect the likelihood of FTDs making a second deposit. This implies that the FTDs' currency does not play a notable role in determining whether FTDs' will make a second deposit.")
}
p9.1 <- paste0("VND FTDs have a <b>", prop$Freq[prop$Var1 == 'VND' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b> likelihood of making a second deposit, IDR FTDs exhibit a high likelihood at <b>",prop$Freq[prop$Var1 == 'IDR' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b>, CNY FTDs follow closely at <b>",prop$Freq[prop$Var1 == 'CNY' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b>, and THB FTDs also show a significant likelihood at <b>",prop$Freq[prop$Var1 == 'THB' & prop$Var2 == 1] |> scales::percent(accuracy = 0.01),"</b> for making second deposits. Thus,  VND and IDR FTDs are more likely to make second deposit having likelihood of more than <b>50%</b>. Importantly, these likelihoods are statistically significant, highlighting the considerable impact of currencies on FTDs' second deposit behavior.")
```
`r paste(p9,p9.1)`


# Conclusions

In conclusion, this comprehensive analysis of First-Time Depositors (FTDs) and their deposit behavior from January 1, 2023, to September 30, 2023, has brought several significant findings to light.

Firstly, the entire population of FTDs was examined, revealing a substantial difference between the first and second deposit amounts. Notably, FTDs' second deposits tended to be higher than their first deposits, indicating a pattern of increased engagement and financial activity among users over time.

The subset of FTDs who made second deposits was also analyzed, showing a consistent trend of lower initial deposit amounts compared to their subsequent deposits. This pattern highlights that FTDs who commit to a second deposit often begin with smaller initial investments and progressively increase their financial engagement.

The analysis revealed that the VIP level plays a crucial role in determining the likelihood of FTDs making a second deposit. Diamond-tier FTDs exhibited a 100.00% likelihood of making a second deposit, and other VIP tiers displayed significant probabilities, emphasizing the influence of VIP status on user loyalty.

Furthermore, the impact of different currencies on FTDs' second deposit behavior was explored. This analysis confirmed that currency significantly affects FTDs' likelihood of making a second deposit, with VND and IDR FTDs demonstrating higher probabilities. These findings underscore the importance of currency preferences in shaping user engagement and financial behavior.

In summary, this analysis provides valuable insights into the factors that influence FTDs' second deposit behavior, highlighting a positive trend in engagement, the influence of VIP levels, and the significance of currency preferences in driving user loyalty and financial participation.


```{r,include=FALSE}
dbDisconnect(duckdb_conn,shutdown = TRUE)

```


